Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-11-11 paper/paper.tex
listening behaviors in humans

Behind the overarching challenge of coming up with a robust predictive model for human listening behaviors, the main practical application of timbre similarity retrieval lies in the emerging topic of computer-assisted instrumentation \cite{maresz2013cmr}.
Following the aesthetic tradition of spectralism in contemporary music creation, the composer queries the machine with an arbitrary audio signal.
The outcome of this query is an instrumental audio sample, alongside textual attributes of playing technique.
In this context, the computer serves as a bridge from the auditory level to the symbolic level, \ie{} from a potentially infinite realm of timbral sensations to a musical score of priorly specified range \cite{caetano2019swarm}.

>>>>

Behind the overarching challenge of coming up with a robust predictive model for listening behaviors in humans, the main practical application of timbre similarity retrieval lies in the emerging topic of computer-assisted instrumentation \cite{maresz2013cmr}.
Following the aesthetic tradition of spectralism in contemporary music creation, the composer queries the machine with an arbitrary audio signal.
The outcome of this query is an instrumental audio sample, alongside textual attributes of playing technique.
In this context, the computer serves as a bridge from the auditory level to the symbolic level, \ie{} from a potentially infinite realm of timbral sensations to a musical score of priorly specified range \cite{caetano2019swarm}.
